\section{Experience}

% \textbf{Data Engineer Intern}, Remote \hfill Jun 2024 – Sep 2024
% \begin{customItem}
% \item Built an automated data pipeline which help faster the cleaning user data, and reduce the inaccuracies by 1.3\%.
% \item Launched a revised customer default model, improving AUC score by \%.
% \item Tools
% \item 
% \end{customItem}

\textbf{Software Engineer Intern}, Wolfram|Alpha, Remote \hfill Jun 2023 – Aug 2023
\begin{customItem}
\item Developed step-by-step functions to solve sums and partial sums of 7 types of series, utilizing Visual Studio Code and Sourcetree, worked within the established framework and protocol of the Wolfram|Alpha Math team.
\item Designed efficient algorithms to handle both standard and novel inputs, ensuring flexibility and accuracy.
\item Conducted rigorous iterative testing to refine the functions, enhancing their robustness and reliability.
\item Initiated pull requests and sought peer reviews, continuously revising the code until achieving unanimous approval. Successfully integrated selected implementations into the Wolfram|Alpha codebase for user access.
\end{customItem}

\vspace{0.1 cm}

\textbf{Graduate Assistant}, University of Maryland, College Park, MD \hfill Sep 2018 – Present
\begin{customItem}
\item Constructed models for integral motivic cohomology with multiple polylogarithms and associated Hodge structures. Proved pertinent theorems. Devised algorithms and developed packages for computations.
% \item Authored and coauthored several scholarly papers focused on motivic models of multiple polylogarithms.
\end{customItem}

\ifthenelse{\boolean{Math}}{

\vspace{0.1 cm}

\textbf{Instructor \& Teaching Assistant}, University of Maryland, College Park, MD \hfill Sep 2018 – Dec 2024
\begin{customItem}
\item Developed comprehensive lecture notes and slides for each class session.
\item Created exams, quizzes, homework assignments, MATLAB projects.
\item Held regular office hours and review sessions.
\item Proficient in using Canvas, Gradescope and Matlab Grader.
\item Managed and maintained my teaching page
\end{customItem}

}{}