\section{Projects}

\ifthenelse{\boolean{Quant} \OR \boolean{DS}}{

\textbf{Home Credit - Credit Risk Model}, Kaggle \hfill Apr 2024 -- May 2024
\begin{customItem}
\item Developed a binary classification model which predict customer loan defaults, maximizing AUC scores.
\item Utilized a custom differentiable loss function based on the Wilcoxon-Mann-Whitney statistic.
\item Conducted correlation analysis on 465 different features, categorized and combined types, eliminated redundancies, and engineered new features, yielding a refined dataset of aggregated features.
\item Constructed an ensemble of LightGBM, XGBoost and CatBoost models with the custom loss function, achieving over 90\% accuracy and an AUC score of 0.80 using the average prediction.
\end{customItem}

}{}

\ifthenelse{\boolean{Quant}\OR \boolean{DS}}{

\vspace{0.1cm}

\textbf{TED Talk Classification}, Johns Hopkins University, INMAS Machine Learning Workshop \hfill Feb 2023 -- Apr 2023
\begin{customItem}
\item Employed the re package for pruning and preprocessing TED talk texts, breaking them into smaller segments.
\item Applied Word2Vec to convert words into vectors and used a bag-of-words model for average representations.
\item Generated 2D graphs of the word vectors, conducting correlation investigation and clustering analyses.
\item Built a three-layered neural network model on 2,000 TED talk texts, capable of labeling them based on categories such as ``Technology'', ``Entertainment'' and ``Design''. Attained approximately 80\% accuracy.
\item Fine-tuned a BERT model for the same classification task, achieving 85\% accuracy and F1 score of 0.78.
\end{customItem}

}{}

% \ifthenelse{\boolean{Quant}}{

% \vspace{0.1cm}

% \textbf{Crypto Market Price Prediction}, INMAS Machine Learning Workshop \hfill Feb 2023 -- Mar 2023
% \begin{customItem}
% \item Built a vector autoregression model to predicts price trends of several cryptocurrencies like Bitcoin, Ethereum.
% \item Established a data pipeline for cleaning and interpolating missing data in daily open, close, high, and end prices.
% \item Conducted stationarity check using Augmented Dickey-Fuller test, obtaining an average $p$-value greater than 0.95.
% \item Utilized AIC to determine optimal lag order, resulting in a reduced average RMSE of 0.19 for price forecasts.
% \end{customItem}

% }{}

\ifthenelse{\boolean{Quant} \OR \boolean{DS}}{

\vspace{0.1cm}

\textbf{Instacart Basket Analysis}, The Erd\H{o}s Institute, Data Science Bootcamp \hfill Sep 2022 -- Dec 2022
\begin{customItem}
\item Performed an in-depth exploratory analysis on 3,000,000 orders from over 20,000 Instacart customers.
\item Employed PCA and KMeans clustering to categorize customers into 3 groups based on their shopping preferences.
\item Developed a customized XGBoost model for each specific customer group, obtained 91\% accuracy predictions based on an appropriate cutoff of the likelihoods of future repurchases of various items.
% \item Delegated tasks into subtasks for every team member and ensured timely and effective communication.
\end{customItem}

}{}