\documentclass[6pt, letterpaper]{article}

% Packages:
\usepackage[
ignoreheadfoot, % set margins without considering header and footer
top=3cm,
bottom=3cm,
left=2cm,
right=2cm,
footskip=1.0cm, % seperation between body and footer
% showframe % for debugging 
]{geometry} % for adjusting page geometry

\usepackage{titlesec} % for customizing section titles
\usepackage{array} % tabularx requires this
\usepackage[dvipsnames]{xcolor} % for coloring text
\usepackage{enumitem} % for customizing lists
\usepackage{amsmath} % for math
\usepackage[
    colorlinks=true,
    urlcolor=black
]{hyperref} % for links
\usepackage{needspace} % for avoiding page brake right after the section title
\usepackage{ifthen} % for conditional statements
\usepackage{iftex} % check if engine is pdflatex, xetex or luatex

% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

% Some settings:
\pagestyle{empty} % no header or footer
\setcounter{secnumdepth}{0} % no section numbering
\setlength{\parindent}{0pt} % no indentation
\setlength{\topskip}{0pt} % no top skip
\pagenumbering{gobble} % no page numbering

\titleformat{\section}{\scshape\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{0pt}{0.2 cm}{0.2 cm} % section title spacing


\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$} % customize bullet points
\newenvironment{customItem}{
\begin{itemize}[
    topsep=0.05 cm,
    parsep=0.05 cm,
    partopsep=0pt,
    itemsep=0pt,
    leftmargin=10pt
]
}{
\end{itemize}
} % customized itemize


% Decide which resume
\newboolean{Quant}
\newboolean{DS}
\newboolean{Math}
\setboolean{Quant}{true}
\setboolean{DS}{false}
\setboolean{Math}{false}


\begin{document}

{\centering

% NAME
\Huge \textbf{Haoran Li} \\

\vspace{.1cm}

% CONTACT
\normalsize
\href{mailto:haoran.li2018@gmail.com}{\textsf{haoran.li2018@gmail.com}}
|
\href{tel:2027796530}{\textsf{(+1)202-779-6530}}
% |
% \href{https://lihaoranicefire.github.io/math/}{\textsf{lihaoranicefire.github.io/math}}
|
\href{https://linkedin.com/in/haoranli2018}{\textsf{linkedin.com/in/haoranli2018}}

}

\section{Education}

\textbf{Ph.D. in Mathematics}, University of Maryland, Graduated Oct 2024 (GPA 4.0/4.0)

\textbf{B.S. in Mathematics and Applied Mathematics}, Sun Yat-sen University, Graduated Jun 2018 (GPA 3.7/4.0)

\section{Skills}

\textbf{Programming:} Python, C\texttt{++}, C, Java, SQL, MATLAB, Git, \LaTeX, Mathematica

\textbf{Skills:} Tensorflow, PyTorch, Keras, Regression analysis, Time series analysis, Credit risk assessment, Stochastic calculus, Derivative pricing, Linux, Git, Excel

\section{Experience}

\textbf{Fixed Income Quant Researcher}, LSEG, New York City \hfill Feb 2025 - Present
\begin{customItem}
\item Submitted change request to codebase, thoroughly tested and successfully integrated into the production release.
\item Conducted P\&L portfolio optimization on corporate bonds, using ex-ante analysis.
\end{customItem}

\textbf{Software Engineer Intern}, Wolfram|Alpha, Remote \hfill Jun 2023 – Aug 2023
\begin{customItem}
\item Developed step-by-step functions to solve sums and partial sums of several types of series, utilizing Visual Studio Code and Sourcetree, worked within the established framework and protocol of the Wolfram|Alpha Math team.
\item Designed efficient algorithms to handle both standard and novel inputs, ensuring flexibility and accuracy.
\item Conducted rigorous iterative testing to refine the functions, enhancing their robustness and reliability.
\item Initiated pull requests and sought peer reviews, continuously revising the code until achieving unanimous approval. Successfully integrated selected implementations into the Wolfram|Alpha codebase for user access.
\end{customItem}

\vspace{0.1 cm}

\textbf{Graduate Assistant}, University of Maryland, College Park, MD \hfill Sep 2018 – Dec 2024
\begin{customItem}
\item Constructed models for integral motivic cohomology with multiple polylogarithms and associated Hodge structures. Proved pertinent theorems. Devised algorithms and developed packages for computations.
% \item Authored and coauthored several scholarly papers focused on motivic models of multiple polylogarithms.
\end{customItem}

\vspace{0.1 cm}

\textbf{Instructor \& Teaching Assistant}, University of Maryland, College Park, MD \hfill Sep 2018 – Dec 2024
\begin{customItem}
\item Developed comprehensive lecture notes and slides. Managed and maintained my teaching page.
\item Proficient in making, grading tests and managing course using Canvas, Gradescope and Matlab Grader.
% \item Created exams, quizzes, homework assignments, MATLAB projects.
\item Held regular office hours and review sessions.
\end{customItem}

\input{Publication.tex}

\section{Awards \& Honors}

\begin{customItem}
\item Dean’s Fellowship, University of Maryland
\item Hauptman Summer Fellowship, University of Maryland
\item Aziz Osborn Gold Medal in Teaching Excellence, University of Maryland
\item Scholarship of Canadian Alumni Association (Hong Kong)
\item First prize on China Undergraduate Mathematical Contest in Modeling (CUMCM-2016)
\item First-Class Scholarships, Sun Yat-sen University
% \item Second prize on the 5th Chinese Mathematics Competitions (CMC)
\end{customItem}

\end{document}